Reflections from reproductions

### 2024-11-04 pages/reflections.qmd
docs(reflections): add johnson 2021 reflections

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | 🟡 | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | 🟡 | ❌ |

@@

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* @huang_optimizing_2019: No changes made.
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
* @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: Add parallel processing, did not run one of the scenarios (it was very long, and hadn't managed to reproduce other parts of same figure regardless), and experimented with reducing parameters for evolutionary algorithm (but, in the end, ran with full parameters, though lower were helpful while working through and troubleshooting).
* @wood_value_2021: No changes made, but unlike other reproduction, didn't try to run at smaller amounts - just set it to run as-is over the weekend.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | 🟡 | 🟡 |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | N/A |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | ❌ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | 🟡 | N/A |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | N/A | N/A |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@@

@@

* @shoaib_simulation_2021: Not relevant (results files **<35 kB**)
* @huang_optimizing_2019: Provided code didn't save results to file. When I saved to file, these were large, so I compressed to `.csv.gz`, which made them small enough that GitHub was still happy (**26 MB**).
* @lim_staff_2020: Provided code didn't save results to file. When I saved to file, these were small, so not relevant (results files **<60 kB**)
* @kim_modelling_2021: Provided code didn't save results to file. When I saved to file, these were small, so not relevant (results files **<1 kB**)
* @anagnostou_facs-charm_2022: Not relevant (results file **34 kB**)
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: Not relevant (aggregate results files **<10 kB**).
* @wood_value_2021: Aggregate results files are small (**327 kB**), but raw results files are very large (**2.38 GB**), and even when compressed to `.csv.gz` (**128 MB**) require using of GitHub LFS

@@

* @shoaib_simulation_2021: Not relevant.
* @huang_optimizing_2019: Not relevant.
* @lim_staff_2020: Not relevant.
* @kim_modelling_2021: Not relevant.
* @anagnostou_facs-charm_2022: Not relevant.
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: The default behaviour of the script was to output **lots of files** from each round (so you could easily have 90, 100, 200+ files), which were then **not** used in analysis (as it just depended on an aggregate results file). Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
* @wood_value_2021: Not relevant.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | ❌ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | 🟡 | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | ❌ | ❌ |

@@

@@

>>>>

<!--TODO: Check all the notes on Johnson's reflections page are captured below, and that there weren't any new categories to add-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |

@@

@johnson_cost_2021: Fully met. Creates a list of `input` which are then used by a `run()` function.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | 🟡 | ❌ | ✅ | N/A | ✅ | 🟡 | ✅ |

@@

@johnson_cost_2021: Fully met. All model parameters could be varied from "outside" the model code itself, as they were provided as changeable inputs to the model.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | N/A | ✅ | ✅ |

@@

@johnson_cost_2021: Not applicable. All inputs defined within script. Outputs are not specifically saved to a file (just that the .md and image files were automatically saved when the .Rmd file was knit).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ❌ | ✅ | ❌ | ✅ | ✅ |

@@

@johnson_cost_2021: Not met. There was alot of duplication when running each scenario. This meant, when amending these for the sensitivity analysis, I would need to change the same parameter 12 times within the script, and for changes to all, changing it 12 times in 14 duplicate scripts. Hence, it was simpler to write an R script to do this than change it directly, but for base case, I had to make sure I carefully changed everything in both files.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | 🟡 | 🟡 | ❌ | 🟡 | ❌ |

@@

@johnson_cost_2021: Not met. Very few comments in the `Case_Detection_Results...Rmd` files, which were the code files provided.

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* @huang_optimizing_2019: No changes made.
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
* @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
* @johnson_cost_2021: Experimented with using a fewer number of agents for troubleshooting (although ultimately had to run with full number to reproduce results), and ran the scripts in parallel by opening seperate terminals simultaneously. Note: Long run time also meant it took a longer time to do this reproduction - although we excluded computation time in our timings, it just meant e.g. when I made a mistake in coding of scenario analysis and had to re-run, I had to wait another day or two for that to finish before I could resume.
* @hernandez_optimal_2015: Add parallel processing, did not run one of the scenarios (it was very long, and hadn't managed to reproduce other parts of same figure regardless), and experimented with reducing parameters for evolutionary algorithm (but, in the end, ran with full parameters, though lower were helpful while working through and troubleshooting).
* @wood_value_2021: No changes made, but unlike other reproduction, didn't try to run at smaller amounts - just set it to run as-is over the weekend.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | N/A | ✅ | 🟡 | 🟡 |

@@

@johnson_cost_2021: Fully met. In the README, they state the the run time with 100 million agents is 16 hours, which was very handy to know, as I then just got stuck in running with fewer agents while troubleshooting.

@@

<!--TODO: Consider whether this should be done like a checklist like this? As actually, I could run a simple version (e.g. serial or one at a time) without issue, but starts taking up more memory with parallel stuff.-->

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | ❌ | N/A | ❌ | <!--TODO--> | N/A |

@@

@johnson_cost_2021: Not met. It becomes more computationally expensive if try to run lots at once in simultaneous terminals. Didn't try running one on local machine with full parameter due to long run time making it infeasible, but knowing my system specs, it should have been able to if did.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | N/A | 🟡 | ❌ | ✅ |

@@

@johnson_cost_2021: Partially met. Has all base case scenarios, but not sensitivity analysis.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ✅ | ✅ |

@@

@johnson_cost_2021: Note met. It has an output that is in "per 1000" and, although it outputs the columns required to calculate this, I found it very tricky to work out which columns to use and how to transform them to get this output, and so feel this is not met (as feels like a seperate output, and not something simple like a mean, and as it felt so tricky to work out).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ✅ | ✅ | ✅ | ❌ | ✅ |

@@

@johnson_cost_2021: Fully met. Base case parameters all correct.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | ✅ | ❌ | ✅ |

@@

@johnson_cost_2021: Fully met. Could determine appropriate parameters for sensitivity analysis from description in article.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | ✅ | 🟡 | N/A |

@@

@johnson_cost_2021: Fully met. All parameters clearly in the two figures presenting the sensitivity analysis, and didn't have to look elsewhere beyond that.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | N/A | N/A | N/A |

@@

@johnson_cost_2021: Not applicable. No processing of parameters required.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | ❌ | ✅ | ✅ |

@@

@johnson_cost_2021: Not met. Outputs to dataframe/s that are not saved as files (although can see within the kept `.md` file from knitting).

@@

@johnson_cost_2021: Not met. I had mistakes and confusion figuring out which results tables I needed, which columns to use, and which scenarios to use from the tables.

@@

* @shoaib_simulation_2021: Not relevant (results files **<35 kB**)
* @huang_optimizing_2019: Provided code didn't save results to file. When I saved to file, these were large, so I compressed to `.csv.gz`, which made them small enough that GitHub was still happy (**26 MB**).
* @lim_staff_2020: Provided code didn't save results to file. When I saved to file, these were small, so not relevant (results files **<60 kB**)
* @kim_modelling_2021: Provided code didn't save results to file. When I saved to file, these were small, so not relevant (results files **<1 kB**)
* @anagnostou_facs-charm_2022: Not relevant (results file **34 kB**)
* @johnson_cost_2021: Provided code didn't save results to file. When I saved to `.csv` files, these were small, so not relevant (results files **<3.6kB**)
* @hernandez_optimal_2015: Not relevant (aggregate results files **<10 kB**).
* @wood_value_2021: Aggregate results files are small (**327 kB**), but raw results files are very large (**2.38 GB**), and even when compressed to `.csv.gz` (**128 MB**) require using of GitHub LFS

@@

* @shoaib_simulation_2021: Not relevant.
* @huang_optimizing_2019: Not relevant.
* @lim_staff_2020: Not relevant.
* @kim_modelling_2021: Not relevant.
* @anagnostou_facs-charm_2022: Not relevant.
* @johnson_cost_2021: Not relevant.
* @hernandez_optimal_2015: The default behaviour of the script was to output **lots of files** from each round (so you could easily have 90, 100, 200+ files), which were then **not** used in analysis (as it just depended on an aggregate results file). Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
* @wood_value_2021: Not relevant.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | ✅ | ✅ | ✅ |

@@

@johnson_cost_2021: Fully met. At start of script, authors `set.seed(333)`.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | ❌ | ❌ | ✅ |

@@

@johnson_cost_2021: Not met. Had to write code to generate tables, which took me a while as I got confused over thinks like which tables / columns / scenarios to use.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | 🟡 | 🟡 | ✅ |

@@

@johnson_cost_2021: Partially met. For Figure 3, most of the required code for the figure was provided, which was super helpful. However, this wasn't complete, and for all others figures, I had to start from scratch writing the code.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | ✅ | ❌ | ❌ |

@@

@johnson_cost_2021: Fully met. README has mini description of model and clear instructions on how to install and run the model.

@@

**Version history and releases**. @johnson_cost_2021 had commits to their GitHub repository after the publication date. It wasn't clear which version aligned with the publication. However, the most recent commits add clear README instructions to the repository. We decided to use the latest version of the repository, but it would have beneficial to have releases/versions/a change log that would help to outline the commit history in relation to the publication and any subsequent changes.

<!--TODO: update or remove this summary-->
